THESIS PROJECT PROPOSAL

### 2019-11-07 project_ashish/paper.tex
Hi modified files

masses robustly suggests new physics beyond Stanard model (BSM). There are lot of specific 

@@

and leptons) couplings are modified. In the effective beyond standard model theory, there are 

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 1}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/tq.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 2}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/newtHq.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 3}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
  \caption{Higgs boson production in association with single top quark in proton collisions}
   \label{figure 5}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms1.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 6}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms2.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 7}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms3.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 8}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms10.png}
  \caption{Elementary particles in standatd model of particle physics}
   \label{figure 9}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 10}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
  \caption{Higgs boson production in association with top quark top anti-quark in proton collisions}
   \label{figure 11}
\end{figure}

>>>>

masses robustly suggests new physics beyond Standard model (BSM). There are lot of specific 

@@

and leptons) couplings are modified. In the effective standard model theory, there are 

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of the Higgs boson in proton collisions.}
   \label{figure 1}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/tq.png}
  \caption{Important production processes of the Higgs boson in proton collisions.}
   \label{figure 2}
\end{figure}

%\begin{figure}
 % \centering
  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/newtHq.png}
 % \caption{Important production processes of the Higgs boson in proton collisions}
  % \label{figure 3}
%\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 4}
\end{figure}

%\begin{figure}
 % \centering
  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
  %\caption{Higgs boson production in association with single top quark in proton collisions}
  % \label{figure 5}
%\end{figure}

%\begin{figure}
 % \centering
  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms1.png}
 % \caption{Important production processes of the Higgs boson in proton collisions}
  % \label{figure 6}
%\end{figure}

%\begin{figure}
 % \centering
  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms2.png}
 % \caption{Important production processes of the Higgs boson in proton collisions}
  % \label{figure 7}
%\end{figure}

%\begin{figure}
 % \centering
  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms3.png}
 % \caption{Important}
  % \label{figure 8}
%\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms10.png}
  \caption{Elementary particles in standard model of particle physics.}
   \label{figure 9}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
  \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
   \label{figure 10}
\end{figure}

%\begin{figure}
 % \centering
  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
 % \caption{Higgs boson production in association with top quark top anti-quark in proton collisions}
  % \label{figure 11}
%\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd.png}
  \caption{Leading order Feynman Diagrams for various Higgs production modes.}
   \label{figure 12}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd1.png}
  \caption{Standard model Higgs boson production cross section in various production modes.}
   \label{figure 13}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd2.png}
  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
   \label{figure 14}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd3.png}
  \caption{Standard model Higgs boson branching ratios in various decay channels.}
   \label{figure 15}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd4.png}
  \caption{Various LHC run and corresponding integrated luminosities.}
   \label{figure 16}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd5.png}
  \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
   \label{figure 17}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd6.png}
  \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
   \label{figure 18}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling modifiers.}
   \label{figure 19}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th.png}
  \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
   \label{figure 20}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th1.png}
  \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
energy.}
   \label{figure 21}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th2.png}
  \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
   \label{figure 22}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th3.png}
  \caption{Lowest order Feynman diagrams for s-channel tH production.}
   \label{figure 22}
\end{figure}
